Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Fixed a missing 'to' in Depth-Masking approach section

The first approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is render the part of the volume directly behind the
intersection, render the intersection itself, and then render the part of the
volume directly in front of the intersection.  Finally the area of the
intersection is masked off and everything else is drawn depth-sorted with
blending enabled.

>>>>

The first approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is to render the part of the volume directly behind the
intersection, render the intersection itself, and then render the part of the
volume directly in front of the intersection.  Finally the area of the
intersection is masked off and everything else is drawn depth-sorted with
blending enabled.
